Demanding resources: Converging perceptions of challenge and resource characteristics

### 2023-07-18 SIOP2024/SIOP2024convergence.Rmd
last bit

tukeytest <- analysis %>% 
  pairwise_t_test(value ~ scale, paired = TRUE, 
                  p.adjust.method = "bonferroni"
                  )  
write.csv(tukeytest, "pairwisets.csv")
psych::describe.by(analysis$value, analysis$scale)

>>>>

tukeytest <- analysis %>% 
  pairwise_t_test(value ~ scale, paired = TRUE, 
                  p.adjust.method = "bonferroni"
                  )  
write.csv(tukeytest, "pairwisets.csv")
#psych::describe.by(analysis$value, analysis$scale)
